---
title: "individual_specialization"
author: "Blanca Arroyo-Correa"
date: "2/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r packages}
library(reshape2)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(igraph)
library(magrittr)
library(bipartite)
library(igraph)

library(r2d3)
library(purrr) 
library(tidyr) 
library(stringr)
library(tibble)
library(RColorBrewer)
library(scales)

library(raster)
library(viridis)
library(ggridges)
library(BBmisc)

library(lubridate)
library(spaa)
library(asbio)
library(pscl)
library(boot)
library(lmerTest)
library(lme4)
library(moments)

library(tidySEM)
library(lavaan)
library(lavaanPlot)
library(IDPmisc)

library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(sjstats)
library(visreg)
library(patchwork)
library(relaimpo)

```

# Read data

The interaction matrix with standardized data is called 'total.int.mat' and it is constructed in the interaction-data-standardization' file. This is the interaction matrix including both video data and transect data.
The 'id' dataset containing information on individual plants was also previously read.


I need to check NAs produced in calculation of metrics

```{r node.level.metrics}

plant.id <- read.csv("Data/individual_plants_id.csv", sep=";")
total.int.mat <- read.csv("Data/complete_interaction_matrix.csv", sep=",")
#ag.int.mat <- read.csv("Data/community_aggregated_matrix.csv", sep=",")

# Distribution of individual plants per species and plot
x <- aggregate(Plant_id ~ Plot + Plant_sp, plant.id, length)
x <- dcast(x, Plot ~ Plant_sp)
rownames(x) <- x[,1]
x[,1] <- NULL
x[is.na(x)] <- 0
x.tot <- colSums(x)
x <- rbind(x, x.tot)


# Color palettes
cols <- data.frame(Plant_sp = sort(unique(unique(plant.id$Plant_sp))), 
                   stringsAsFactors = F)
cols2 <- cbind(cols, data.frame(color = c("#a6cee3",
"#1f78b4",
"#b2df8a",
"#33a02c",
"#fb9a99",
"#e31a1c",
"#fdbf6f",
"#ff7f00",
"#cab2d6",
"#6a3d9a",
"grey50")))

cols2 <- cbind(cols, data.frame(color = c("cadetblue3", "dodgerblue3",
                                          "burlywood2", 
                                          "lightpink1", "brown2", 
                                          "darkolivegreen3", "forestgreen", 
                                          "orange", "darkorange2", "gray70", 
                                          "burlywood4")))

cols2 <- setNames((cols2$color), cols$Plant_sp)

complete.matrix <- merge(total.int.mat, plant.id[,c(3,5)], by="Plant_id")


```

# Calculate individual-level metrics

Topological metrics were calculated for each individual plant within its individual-based network.

```{r ind.metrics}

matrix.per.sp <- split(complete.matrix, complete.matrix$Plant_sp)
matrix.per.sp2 <- lapply(matrix.per.sp, function(i) i %>% dplyr::select(-Plant_sp))

metrics.per.sp <- list()


for (i in 1:length(matrix.per.sp2)) {
  temp <- matrix.per.sp2[[i]][, -1] # remove Plant_id column
  temp <- round(temp*1000, 0)
  temp %<>% select_if(colSums(.) != 0) # remove non interacting pollinators
  
  # Calculate node-level metrics
  temp2 <- specieslevel(temp, 
                       level = "lower", index = c("degree", "species strength", "closeness")) 
  
  temp2$weighted.degree <- rowSums(temp)
  
  # Niche overlap
  temp.mat <- matrix.per.sp2[[i]][2:ncol(matrix.per.sp2[[i]])]
  row.names(temp.mat) <- matrix.per.sp2[[i]]$Plant_id
  jaccard.index <- as.matrix(proxy::simil(temp.mat, method = "bray"))
  jaccard.index <- melt(jaccard.index, varnames = c("ind_1", "ind_2"))
  jaccard.index <- aggregate(value ~ ind_1, jaccard.index, mean)
  
  temp2$niche.overlap <- jaccard.index$value
  
  # Partner evenness
  H <- vegan::diversity(matrix.per.sp2[[i]][2:ncol(matrix.per.sp2[[i]])])
  S <- vegan::specnumber(matrix.per.sp2[[i]][2:ncol(matrix.per.sp2[[i]])])
  J <- H/log(S)
  
  temp2$evenness <- J

  temp2$Plant_id <- matrix.per.sp2[[i]]$Plant_id
  metrics.per.sp[[i]] <- temp2
}

metrics <- bind_rows(metrics.per.sp)
metrics[is.na(metrics)] <- 0
metrics$closeness <- NULL
names(metrics)[names(metrics) == 'species.strength'] <- 'strength'
names(metrics)[names(metrics) == 'degree'] <- 'normalised.degree'

metrics <- merge(plant.id[,5, drop=FALSE], metrics, by="Plant_id", all.x=T)
metrics[is.na(metrics)] <- 0

# plot
metrics.id.sp <- merge(metrics, plant.id[,c(3,5)], by="Plant_id")
metrics.id.sp.long <- melt(metrics.id.sp, id.vars=c("Plant_id", "Plant_sp"))
str(metrics.id.sp.long)


metrics.id.sp.long <- metrics.id.sp.long %>%
  filter(Plant_sp != "CSAL", Plant_sp != "UPAR",
         variable %in% c("normalised.degree",
                         "strength",
                         "weighted.closeness",
                         "niche.overlap")) %>% droplevels

```


# Plant traits

```{r traits}

non.recorded.plants <- read.csv("Data/RBD_interaction_data_20220307.csv", sep=";")

plant.id <- read.csv("Data/individual_plants_id.csv", sep=";")
recorded.plants <- read.csv("Data/RBD_video_processing_20220307.csv", sep=";")

flower.data.1 <- unique(dplyr::select(non.recorded.plants, c(Plot, Week, Plant_sp, Plant_id, N_flowers)))
flower.data.2 <- unique(dplyr::select(recorded.plants, c(Plot, Week, Plant_sp, Plant_id, N_flowers)))

flower.data <- rbind(flower.data.1, flower.data.2)
flower.data$N_flowers <- as.numeric(flower.data$N_flowers)

# total number of flowers

flower.data <- aggregate(N_flowers ~ Plant_id + Plant_sp + Plot, flower.data, sum)

flower.data <- merge(flower.data, plant.id, by=c("Plant_id", "Plant_sp", "Plot"), all.x = T)

flower.data$Plant_id[duplicated(flower.data$Plant_id)]


plant.area <- read.csv("Data/Plant_traits/Plant_size/individual_plant_area.csv", sep=";") %>% 
  dplyr::select(Plant_id, Area_m2)

plant.height <- read.csv("Data/Plant_traits/Plant_size/individual_plant_height.csv", sep=";") %>% 
  dplyr::select(Plant_id, Height_cm)

plant.traits <- merge(plant.id, flower.data[, c(1,4)], by="Plant_id", all.x=T)
plant.traits[is.na(plant.traits)] <- 0

plant.traits <- merge(plant.traits, plant.area, by="Plant_id")
plant.traits <- merge(plant.traits, plant.height, by="Plant_id")

cor.test(plant.traits$Area_m2, plant.traits$Height_cm)
plot(plant.traits$Area_m2, plant.traits$Height_cm)

cor.test(plant.traits$Area_m2, plant.traits$N_flowers)
plot(plant.traits$Area_m2, plant.traits$N_flowers)

cor.test(plant.traits$Height_cm, plant.traits$N_flowers)
plot(plant.traits$Height_cm, plant.traits$N_flowers)

# Flowering synchrony
synchrony.index <- read.csv("Data/Plant_traits/flowering_synchrony_plants.csv", sep=",")

plant.traits <- merge(plant.traits, synchrony.index[,c(1,3:4)], 
                      by="Plant_id", all.x = T)

all.data <- merge(plant.traits, metrics, by="Plant_id")

plant.traits[rowSums(is.na(plant.traits)) > 0, ]

# Neighbourhood cover
cover.neigh <- read.csv("Data/Plant_traits/neighbourhood_plants.csv", sep=",")

plant.traits <- merge(plant.traits, cover.neigh[,c(1,3:4)], 
                      by="Plant_id", all.x = T)

#write.csv(plant.traits,"Data/all_plant_traits.csv", row.names = FALSE)

all.plant.data <- merge(plant.traits, metrics, by="Plant_id")

cor.test(all.plant.data$Height_cm, all.plant.data$N_flowers)
plot(all.plant.data$Height_cm, all.plant.data$N_flowers)

cor.test(all.plant.data$Area_m2, all.plant.data$N_flowers)
plot(all.plant.data$Area_m2, all.plant.data$N_flowers)


```



# Generalized Linear Models (overall)

```{r glm}

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
all.data.norm <- as.data.frame(lapply(na.omit(all.plant.data[, c(6, 8:18)]), range01))

all.data.norm <- cbind(plant.id[, c(2,3,5)], all.data.norm) # include plant_id and sp

all.data.norm <- all.data.norm %>%
  filter(Plant_sp != "CSAL", Plant_sp != "UPAR") %>%
  droplevels

### OVERALL MODELS

## GLMM with random intercept

# Normalised degree
hist(log(all.plant.data$normalised.degree))
model.degree <- lmer(log(normalised.degree+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                       range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) +
                       (1|Plant_sp),
                    data=all.data.norm)

summary(model.degree)
plot(model.degree)
confint(model.degree)
coef(model.degree)$Plant_sp # Estimates of the random effects (intercepts of Plant sp)
r2(model.degree)


# Strength
hist(log(all.plant.data$strength))
model.strength <- lmer((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) +
                       (1|Plant_sp),
                    data=all.data.norm)

summary(model.strength)
plot(model.strength)
confint(model.strength)
coef(model.strength)$Plant_sp # Estimates of the random effects (intercepts of Plant sp)
r2(model.strength)


# Weighted closeness
hist(log(all.plant.data$weighted.closeness))

model.weighted.closeness <- lmer(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) +
                       (1|Plant_sp),
                    data=all.data.norm)

summary(model.weighted.closeness)
plot(model.weighted.closeness)
confint(model.weighted.closeness)
coef(model.weighted.closeness)$Plant_sp # Estimates of the random effects (intercepts of Plant sp)
r2(model.weighted.closeness)

# Niche overlap
hist(log(all.plant.data$niche.overlap))

model.niche.overlap <- lmer(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) +
                       (1|Plant_sp),
                    data=all.data.norm)

summary(model.niche.overlap)
plot(model.niche.overlap)
confint(model.niche.overlap)
coef(model.niche.overlap)$Plant_sp # Estimates of the random effects (intercepts of Plant sp)
r2(model.niche.overlap)


# Model fit

plot(model.strength, resid(., scaled=TRUE) ~ fitted(.), abline = 0,pch=16,xlab="Fitted values",ylab="Standardised residuals")

plot(model.strength, resid(., scaled=TRUE) ~ fitted(.)| Plant_sp, abline = 0,pch=16,xlab="Fitted values",ylab="Standardised residuals")

plot(model.strength, as.factor(Plant_sp) ~ resid(., scaled=TRUE),abline=0,pch=16,xlab="Standardised residuals",ylab="Regions")

qqnorm(resid(model.strength),pch=16)
qqline(resid(model.strength))



tab_model(
  model.degree, model.strength, model.weighted.closeness, model.niche.overlap,
  dv.labels = c("Normalised degree", "Strength", "Weighted closeness", "Niche overlap"),
  pred.labels = c("Intercept", "Number of flowers", "Height (cm)", 
          "Conspecific flowering synchrony", "Heterospecific flowering synchrony",
          "Conspecific neighborhood cover", "Heterospecific neighborhood cover"),
  string.pred = "Coefficient",
  string.ci = "CI (95%)",
  string.est = "Estimate",
  string.p = "P-Value", digits.p = 2
)



```

# Generalized Linear Models (for each species) -  degree

```{r glm}

## AVEL
hist(log(filter(all.data.norm, Plant_sp== "AVEL")$normalised.degree))
model.degree.AVEL <- lm((log(normalised.degree+1)) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) ,
                    data=filter(all.data.norm, Plant_sp== "AVEL"))

summary(model.degree.AVEL)
r2(model.degree.AVEL)


## CLIB
model.degree.CLIB <- lm((log(normalised.degree+1)) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het)+ range01(Cover_con) + range01(Cover_het) ,
                    data=filter(all.data.norm, Plant_sp== "CLIB"))

summary(model.degree.CLIB)

## HCOM
model.degree.HCOM <- lm((log(normalised.degree+1)) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HCOM"))

summary(model.degree.HCOM)

## HHAL
model.degree.HHAL <- lm((log(normalised.degree+1)) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HHAL"))

summary(model.degree.HHAL)

## HPIC
model.degree.HPIC <- lm((log(normalised.degree+1)) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) ,
                    data=filter(all.data.norm, Plant_sp== "HPIC"))

summary(model.degree.HPIC)

## LPED
model.degree.LPED <- lm(log(normalised.degree+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) ,
                    data=filter(all.data.norm, Plant_sp== "LPED"))

summary(model.degree.LPED)

## ROFF
model.degree.ROFF <- lm(log(normalised.degree+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "ROFF"))

summary(model.degree.ROFF)

## SGEN
model.degree.SGEN <- lm(log(normalised.degree+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "SGEN"))

summary(model.degree.SGEN)

## TMAS
model.degree.TMAS <- lm(log(normalised.degree+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "TMAS"))

summary(model.degree.TMAS)


# Combine all models

tab_model(
  model.degree.AVEL, model.degree.CLIB, model.degree.HCOM, 
  model.degree.HHAL,model.degree.HPIC, model.degree.LPED, 
  model.degree.ROFF, model.degree.SGEN, model.degree.TMAS, 
  dv.labels = c("AVEL", "CLIB", "HCOM", "HHAL","HPIC", "LPED", "ROFF", "SGEN","TMAS"),
  pred.labels = c("Intercept", "Number of flowers", "Height (cm)", 
          "Conspecific flowering synchrony", "Heterospecific flowering synchrony",
          "Conspecific neighborhood cover", "Heterospecific neighborhood cover"),
  string.pred = "Coefficient",
  string.ci = "CI (95%)",
  string.est = "Estimate",
  string.p = "P-Value", digits.p = 2,
  show.p=T
)



full.plot.degree <- sjPlot::plot_models(
  model.degree.AVEL, model.degree.CLIB, model.degree.HCOM, 
  model.degree.HHAL, model.degree.HPIC, model.degree.LPED, 
  model.degree.ROFF, model.degree.SGEN, model.degree.TMAS,
  spacing = 0.7, dot.size=1.2, line.size = 0.4, vline.color="grey80") +
  scale_color_manual(values = c("gray70","darkorange2","orange",
                                "forestgreen","darkolivegreen3","brown2",
                                "lightpink1","dodgerblue3","cadetblue3"),
                     labels=c("TMAS", "SGEN", "ROFF", 
                              "LPED", "HPIC", "HHAL", 
                              "HCOM", "CLIB", "AVEL")) +
  theme_minimal(base_size = 4) + ylab("Coefficient estimate") + xlab("") +
  labs(title="Degree") +
  theme(axis.text=element_text(size=11),
       plot.title = element_text(size=12, 
                                 margin = margin(t = 0, r = 0, b = 15, l = 0),
                                 face="bold"),
       axis.title=element_text(size=14), 
       legend.text = element_text(size=12), legend.title=element_blank(),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
       axis.text.y=element_text(margin=margin(t = 0, r = 10, b = 0, l = 0)),
       axis.text.x=element_text(margin=margin(t = 10, r = 0, b = 0, l = 0))) +
  scale_x_discrete(expand=c(0.1, 0.1), labels=c("range01(N_flowers)" = "Number of flowers",
                         "range01(Height_cm)" = "Height",
                         "range01(sync_index_con)" = "Flowering synchrony (C)",
                         "range01(sync_index_het)" = "Flowering synchrony (H)",
                         "range01(Cover_con)" = "Neigborhood cover (C)",
                         "range01(Cover_het)" = "Neigborhood cover (H)")) + 
  coord_flip(ylim = c(-0.65, 0.65)) +
  scale_y_continuous(breaks = seq(-0.65, 0.65, by = 0.3))


lmg.degree <- as.data.frame(cbind(calc.relimp(model.degree.AVEL, rela=T)$lmg,
calc.relimp(model.degree.CLIB, rela=T)$lmg,
calc.relimp(model.degree.HCOM, rela=T)$lmg,
calc.relimp(model.degree.HHAL, rela=T)$lmg, 
calc.relimp(model.degree.HPIC, rela=T)$lmg, 
calc.relimp(model.degree.LPED, rela=T)$lmg,
calc.relimp(model.degree.ROFF, rela=T)$lmg, 
calc.relimp(model.degree.SGEN, rela=T)$lmg, 
calc.relimp(model.degree.TMAS, rela=T)$lmg))

lmg.degree$trait <- rownames(lmg.degree)
lmg.degree <- melt(lmg.degree, id.vars="trait")
lmg.degree <- as.data.frame(as.matrix(aggregate(value ~ trait, lmg.degree, function(x) c(mean = mean(x), sd = sd(x) ))))
names(lmg.degree) <- c("trait", "degree.mean", "degree.sd")



```

# Generalized Linear Models (for each species) - Strength

```{r glm}

## AVEL
hist(log(filter(na.omit(all.data.norm), Plant_sp== "AVEL")$strength))
model.strength.AVEL <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "AVEL"))

summary(model.strength.AVEL)

## CLIB
hist(log(filter(na.omit(all.data.norm), Plant_sp== "CLIB")$strength))
model.strength.CLIB <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "CLIB"))

summary(model.strength.CLIB)

## HCOM
hist(log(filter(na.omit(all.data.norm), Plant_sp== "HCOM")$strength))
model.strength.HCOM <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HCOM"))

summary(model.strength.HCOM)

## HHAL
hist(log(filter(na.omit(all.data.norm), Plant_sp== "HHAL")$strength))
model.strength.HHAL <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HHAL"))

summary(model.strength.HHAL)

## HPIC
hist(log(filter(na.omit(all.data.norm), Plant_sp== "HPIC")$strength))
model.strength.HPIC <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HPIC"))

summary(model.strength.HPIC)

## LPED
hist(log(filter(na.omit(all.data.norm), Plant_sp== "LPED")$strength))
model.strength.LPED <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "LPED"))

summary(model.strength.LPED)

## ROFF
hist(log(filter(na.omit(all.data.norm), Plant_sp== "ROFF")$strength))
model.strength.ROFF <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "ROFF"))

summary(model.strength.ROFF)

## SGEN
hist(log(filter(na.omit(all.data.norm), Plant_sp== "SGEN")$strength))
model.strength.SGEN <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "SGEN"))

summary(model.strength.SGEN)

## TMAS
hist(log(filter(na.omit(all.data.norm), Plant_sp== "TMAS")$strength))
model.strength.TMAS <- lm((log(strength+1)) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "TMAS"))

summary(model.strength.TMAS)

# Combine all models

tab_model(
  model.strength.AVEL, model.strength.CLIB, model.strength.HCOM, 
  model.strength.HHAL, model.strength.HPIC, model.strength.LPED, 
  model.strength.ROFF, model.strength.SGEN, model.strength.TMAS, 
  dv.labels = c("AVEL", "CLIB", "HCOM", "HHAL","HPIC", "LPED", "ROFF", "SGEN","TMAS"),
  pred.labels = c("Intercept", "Number of flowers", "Height (cm)", 
          "Conspecific flowering synchrony", "Heterospecific flowering synchrony",
          "Conspecific neighborhood cover", "Heterospecific neighborhood cover"),
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value", digits.p = 2
)


full.plot.strength <- sjPlot::plot_models(
  model.strength.AVEL, model.strength.CLIB, model.strength.HCOM, 
  model.strength.HHAL, model.strength.HPIC, model.strength.LPED, 
  model.strength.ROFF, model.strength.SGEN, model.strength.TMAS,
  spacing = 0.7, dot.size=1.2, line.size = 0.4, vline.color="grey80")  +
  scale_color_manual(values = c("gray70","darkorange2","orange",
                                "forestgreen","darkolivegreen3","brown2",
                                "lightpink1","dodgerblue3","cadetblue3"),
                     labels=c("TMAS", "SGEN", "ROFF", 
                              "LPED", "HPIC", "HHAL", 
                              "HCOM", "CLIB", "AVEL")) +
  theme_minimal(base_size = 4) + ylab("Coefficient estimate") + xlab("") +
  labs(title="(B) Strength") +
  theme(axis.text=element_text(size=11),
       plot.title = element_text(size=12, 
                                 margin = margin(t = 0, r = 0, b = 15, l = 0),
                                 face="bold"),
       axis.title=element_text(size=14), 
       legend.text = element_text(size=15), legend.title=element_blank(),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
       axis.text.y=element_text(margin=margin(t = 0, r = 10, b = 0, l = 0)),
       axis.text.x=element_text(margin=margin(t = 10, r = 0, b = 0, l = 0))) +
  scale_x_discrete(expand=c(0.1, 0.1), labels=c("range01(N_flowers)" = "Number of flowers",
                         "range01(Height_cm)" = "Height",
                         "range01(sync_index_con)" = "Flowering synchrony (C)",
                         "range01(sync_index_het)" = "Flowering synchrony (H)",
                         "range01(Cover_con)" = "Neigborhood cover (C)",
                         "range01(Cover_het)" = "Neigborhood cover (H)")) + 
  coord_flip(ylim = c(-0.7, 0.7)) +
  scale_y_continuous(breaks = seq(-0.7, 0.7, by = 0.3))

lmg.strength <- as.data.frame(cbind(calc.relimp(model.strength.AVEL, rela=T)$lmg,
calc.relimp(model.strength.CLIB, rela=T)$lmg,
calc.relimp(model.strength.HCOM, rela=T)$lmg,
calc.relimp(model.strength.HHAL, rela=T)$lmg, 
calc.relimp(model.strength.HPIC, rela=T)$lmg, 
calc.relimp(model.strength.LPED, rela=T)$lmg,
calc.relimp(model.strength.ROFF, rela=T)$lmg, 
calc.relimp(model.strength.SGEN, rela=T)$lmg, 
calc.relimp(model.strength.TMAS, rela=T)$lmg))

lmg.strength$trait <- rownames(lmg.strength)
lmg.strength <- melt(lmg.strength, id.vars="trait")
lmg.strength <- as.data.frame(as.matrix(aggregate(value ~ trait, lmg.strength, function(x) c(mean = mean(x), sd = sd(x) ))))
names(lmg.strength) <- c("trait", "strength.mean", "strength.sd")

```

# Generalized Linear Models (for each species) - Weighted closeness

```{r glm}

## AVEL
model.closeness.AVEL <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "AVEL"))

summary(model.closeness.AVEL)

## CLIB
model.closeness.CLIB <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "CLIB"))

summary(model.closeness.CLIB)

## HCOM
model.closeness.HCOM <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "HCOM"))

summary(model.closeness.HCOM)

## HHAL
model.closeness.HHAL <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "HHAL"))

summary(model.closeness.HHAL)

## HPIC
model.closeness.HPIC <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "HPIC"))

summary(model.closeness.HPIC)

## LPED
model.closeness.LPED <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "LPED"))

summary(model.closeness.LPED)

## ROFF
model.closeness.ROFF <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "ROFF"))

summary(model.closeness.ROFF)

## SGEN
model.closeness.SGEN <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "SGEN"))

summary(model.closeness.SGEN)

## TMAS
model.closeness.TMAS <- lm(log(weighted.closeness+1) ~ 
                      range01(N_flowers) + range01(Height_cm) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter((all.data.norm), Plant_sp== "TMAS"))

summary(model.closeness.TMAS)

# Combine all models

tab_model(
  model.closeness.AVEL, model.closeness.CLIB, model.closeness.HCOM, 
  model.closeness.HHAL, model.closeness.HPIC, model.closeness.LPED, 
  model.closeness.ROFF, model.closeness.SGEN, model.closeness.TMAS, 
  dv.labels = c("AVEL", "CLIB", "HCOM", "HHAL","HPIC", "LPED", "ROFF", "SGEN","TMAS"),
  pred.labels = c("Intercept", "Number of flowers", "Height (cm)", 
          "Conspecific flowering synchrony", "Heterospecific flowering synchrony",
          "Conspecific neighborhood cover", "Heterospecific neighborhood cover"),
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value", digits.p = 2
)


full.plot.closeness <- sjPlot::plot_models(
  model.closeness.AVEL, model.closeness.CLIB, model.closeness.HCOM, 
  model.closeness.HHAL, model.closeness.HPIC, model.closeness.LPED, 
  model.closeness.ROFF, model.closeness.SGEN, model.closeness.TMAS,
  spacing = 0.7, dot.size=1.2, line.size = 0.4, vline.color="grey80") +
  scale_color_manual(values = c("gray70","darkorange2","orange",
                                "forestgreen","darkolivegreen3","brown2",
                                "lightpink1","dodgerblue3","cadetblue3"),
                     labels=c("TMAS", "SGEN", "ROFF", 
                              "LPED", "HPIC", "HHAL", 
                              "HCOM", "CLIB", "AVEL")) +
  theme_minimal(base_size = 4) + ylab("Coefficient estimate") + xlab("") +
  labs(title="(C) Weighted closeness") +
  theme(axis.text=element_text(size=11),
       plot.title = element_text(size=12, 
                                 margin = margin(t = 0, r = 0, b = 15, l = 0),
                                 face="bold"),
       axis.title=element_text(size=14), 
       legend.text = element_text(size=15), legend.title=element_blank(),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
       axis.text.y=element_text(margin=margin(t = 0, r = 10, b = 0, l = 0)),
       axis.text.x=element_text(margin=margin(t = 10, r = 0, b = 0, l = 0))) +
  scale_x_discrete(expand=c(0.1, 0.1), labels=c("range01(N_flowers)" = "Number of flowers",
                         "range01(Height_cm)" = "Height",
                         "range01(sync_index_con)" = "Flowering synchrony (C)",
                         "range01(sync_index_het)" = "Flowering synchrony (H)",
                         "range01(Cover_con)" = "Neigborhood cover (C)",
                         "range01(Cover_het)" = "Neigborhood cover (H)")) + 
  coord_flip(ylim = c(-0.20, 0.20)) +
  scale_y_continuous(breaks = seq(-0.20, 0.20, by = 0.1))


lmg.closeness <- as.data.frame(cbind(calc.relimp(model.closeness.AVEL, rela=T)$lmg,
calc.relimp(model.closeness.CLIB, rela=T)$lmg,
calc.relimp(model.closeness.HCOM, rela=T)$lmg,
calc.relimp(model.closeness.HHAL, rela=T)$lmg, 
calc.relimp(model.closeness.HPIC, rela=T)$lmg, 
calc.relimp(model.closeness.LPED, rela=T)$lmg,
calc.relimp(model.closeness.ROFF, rela=T)$lmg, 
calc.relimp(model.closeness.SGEN, rela=T)$lmg, 
calc.relimp(model.closeness.TMAS, rela=T)$lmg))

lmg.closeness$trait <- rownames(lmg.closeness)
lmg.closeness <- melt(lmg.closeness, id.vars="trait")
lmg.closeness <- as.data.frame(as.matrix(aggregate(value ~ trait, lmg.closeness, function(x) c(mean = mean(x), sd = sd(x) ))))
names(lmg.closeness) <- c("trait", "closeness.mean", "closeness.sd")


```

# Generalized Linear Models (for each species) - Niche overlap

```{r glm}


## AVEL
hist((filter(na.omit(all.data.norm), Plant_sp== "AVEL")$niche.overlap))
model.niche.overlap.AVEL <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het), 
                    data=filter(all.data.norm, Plant_sp== "AVEL"))

summary(model.niche.overlap.AVEL)

## CLIB
hist((filter(na.omit(all.data.norm), Plant_sp== "CLIB")$niche.overlap))
model.niche.overlap.CLIB <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "CLIB"))

summary(model.niche.overlap.CLIB)

## HCOM
hist((filter(na.omit(all.data.norm), Plant_sp== "HCOM")$niche.overlap))
model.niche.overlap.HCOM <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het) ,
                    data=filter(all.data.norm, Plant_sp== "HCOM"))

summary(model.niche.overlap.HCOM)

## HHAL
hist((filter(na.omit(all.data.norm), Plant_sp== "HHAL")$niche.overlap))
model.niche.overlap.HHAL <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HHAL"))

summary(model.niche.overlap.HHAL)

## HPIC
hist((filter(na.omit(all.data.norm), Plant_sp== "HPIC")$niche.overlap))
model.niche.overlap.HPIC <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "HPIC"))

summary(model.niche.overlap.HPIC)

## LPED
hist((filter(na.omit(all.data.norm), Plant_sp== "LPED")$niche.overlap))
model.niche.overlap.LPED <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "LPED"))

summary(model.niche.overlap.LPED)

## ROFF
hist((filter(na.omit(all.data.norm), Plant_sp== "ROFF")$niche.overlap))
model.niche.overlap.ROFF <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "ROFF"))

summary(model.niche.overlap.ROFF)

## SGEN
hist((filter(na.omit(all.data.norm), Plant_sp== "SGEN")$niche.overlap))
model.niche.overlap.SGEN <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "SGEN"))

summary(model.niche.overlap.SGEN)

## TMAS
hist((filter(na.omit(all.data.norm), Plant_sp== "TMAS")$niche.overlap))
model.niche.overlap.TMAS <- lm(log(niche.overlap+1) ~ 
                      range01(N_flowers) + range01(sync_index_con) +
                        range01(sync_index_het) + range01(Cover_con) + range01(Cover_het),
                    data=filter(all.data.norm, Plant_sp== "TMAS"))

summary(model.niche.overlap.TMAS)

# Combine all models

tab_model(
  model.niche.overlap.AVEL, model.niche.overlap.CLIB, model.niche.overlap.HCOM, 
  model.niche.overlap.HHAL, model.niche.overlap.HPIC, model.niche.overlap.LPED, 
  model.niche.overlap.ROFF, model.niche.overlap.SGEN, model.niche.overlap.TMAS, 
  dv.labels = c("AVEL", "CLIB", "HCOM", "HHAL","HPIC", "LPED", "ROFF", "SGEN","TMAS"),
  pred.labels = c("Intercept", "Number of flowers", 
          "Conspecific flowering synchrony", "Heterospecific flowering synchrony",
          "Conspecific neighborhood cover", "Heterospecific neighborhood cover"),
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value", digits.p = 2
)


full.plot.nicheoverlap <- sjPlot::plot_models(
  model.niche.overlap.AVEL, model.niche.overlap.CLIB, model.niche.overlap.HCOM, 
  model.niche.overlap.HHAL, model.niche.overlap.HPIC, model.niche.overlap.LPED, 
  model.niche.overlap.ROFF, model.niche.overlap.SGEN, model.niche.overlap.TMAS,
  spacing = 0.7, dot.size=1.2, line.size = 0.4, vline.color="grey80") +
  scale_color_manual(values = c("gray70","darkorange2","orange",
                                "forestgreen","darkolivegreen3","brown2",
                                "lightpink1","dodgerblue3","cadetblue3"),
                     labels=c("TMAS", "SGEN", "ROFF", 
                              "LPED", "HPIC", "HHAL", 
                              "HCOM", "CLIB", "AVEL")) +
  theme_minimal(base_size = 4) + ylab("Coefficient estimate") + xlab("") +
  labs(title="Niche overlap") +
  theme(axis.text=element_text(size=11),
       plot.title = element_text(size=12, 
                                 margin = margin(t = 0, r = 0, b = 15, l = 0),
                                 face="bold"),
       axis.title=element_text(size=14), 
       legend.text = element_text(size=15), legend.title=element_blank(),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
       axis.text.y=element_text(margin=margin(t = 0, r = 10, b = 0, l = 0)),
       axis.text.x=element_text(margin=margin(t = 10, r = 0, b = 0, l = 0))) +
  scale_x_discrete(expand=c(0.1, 0.1), labels=c("range01(N_flowers)" = "Number of flowers",
                         "range01(Height_cm)" = "Height",
                         "range01(sync_index_con)" = "Flowering synchrony (C)",
                         "range01(sync_index_het)" = "Flowering synchrony (H)",
                         "range01(Cover_con)" = "Neigborhood cover (C)",
                         "range01(Cover_het)" = "Neigborhood cover (H)")) + 
  coord_flip(ylim = c(-1, 1)) +
  scale_y_continuous(breaks = seq(-1, 1, by = 0.5))



lmg.niche.overlap <- as.data.frame(cbind(calc.relimp(model.niche.overlap.AVEL, rela=T)$lmg,
calc.relimp(model.niche.overlap.CLIB, rela=T)$lmg,
calc.relimp(model.niche.overlap.HCOM, rela=T)$lmg,
calc.relimp(model.niche.overlap.HHAL, rela=T)$lmg, 
calc.relimp(model.niche.overlap.HPIC, rela=T)$lmg, 
calc.relimp(model.niche.overlap.LPED, rela=T)$lmg,
calc.relimp(model.niche.overlap.ROFF, rela=T)$lmg, 
calc.relimp(model.niche.overlap.SGEN, rela=T)$lmg, 
calc.relimp(model.niche.overlap.TMAS, rela=T)$lmg))

lmg.niche.overlap$trait <- rownames(lmg.niche.overlap)
lmg.niche.overlap <- melt(lmg.niche.overlap, id.vars="trait")
lmg.niche.overlap <- as.data.frame(as.matrix(aggregate(value ~ trait, lmg.niche.overlap, function(x) c(mean = mean(x), sd = sd(x) ))))
names(lmg.niche.overlap) <- c("trait", "niche.overlap.mean", "niche.overlap.sd")


lmg.d.no <- merge(lmg.degree, lmg.niche.overlap, by="trait")

lmg.d.no <- lmg.d.no %>% mutate_at((names(lmg.d.no)[2:5]), as.numeric)
str(lmg.d.no)

lmg.d.no %<>% mutate_if(is.numeric, ~ . * 100)
lmg.d.no %>% mutate_if(is.numeric, round, digits=2)


# plot

full.plot.degree + full.plot.nicheoverlap + full.plot.strength + full.plot.closeness + 
  plot_layout(ncol = 4)


```

```{r model.diag}

# DEGREE
plot(model.degree.AVEL)
plot(model.degree.CLIB)
plot(model.degree.HCOM)
plot(model.degree.HHAL)
plot(model.degree.HPIC)
plot(model.degree.LPED)
plot(model.degree.ROFF)
plot(model.degree.SGEN)
plot(model.degree.TMAS)

lattice::qqmath(model.degree.AVEL)
lattice::qqmath(model.degree.CLIB)
lattice::qqmath(model.degree.HCOM)
lattice::qqmath(model.degree.HHAL)
lattice::qqmath(model.degree.HPIC)
lattice::qqmath(model.degree.LPED)
lattice::qqmath(model.degree.ROFF)
lattice::qqmath(model.degree.SGEN)
lattice::qqmath(model.degree.TMAS)

# squared correlation between the response variable and the predicted values
cor(model.response(model.frame(model.degree.AVEL)),predict(model.degree.AVEL,type="response"))^2
cor(model.response(model.frame(model.degree.CLIB)),predict(model.degree.CLIB,type="response"))^2
cor(model.response(model.frame(model.degree.HCOM)),predict(model.degree.HCOM,type="response"))^2
cor(model.response(model.frame(model.degree.HHAL)),predict(model.degree.HHAL,type="response"))^2
cor(model.response(model.frame(model.degree.HPIC)),predict(model.degree.HPIC,type="response"))^2
cor(model.response(model.frame(model.degree.LPED)),predict(model.degree.LPED,type="response"))^2
cor(model.response(model.frame(model.degree.ROFF)),predict(model.degree.ROFF,type="response"))^2
cor(model.response(model.frame(model.degree.SGEN)),predict(model.degree.SGEN,type="response"))^2
cor(model.response(model.frame(model.degree.TMAS)),predict(model.degree.TMAS,type="response"))^2


# STRENGTH
plot(model.strength.AVEL)
plot(model.strength.CLIB)
plot(model.strength.HCOM)
plot(model.strength.HHAL)
plot(model.strength.HPIC)
plot(model.strength.LPED)
plot(model.strength.ROFF)
plot(model.strength.SGEN)
plot(model.strength.TMAS)

lattice::qqmath(model.strength.AVEL)
lattice::qqmath(model.strength.CLIB)
lattice::qqmath(model.strength.HCOM)
lattice::qqmath(model.strength.HHAL)
lattice::qqmath(model.strength.HPIC)
lattice::qqmath(model.strength.LPED)
lattice::qqmath(model.strength.ROFF)
lattice::qqmath(model.strength.SGEN)
lattice::qqmath(model.strength.TMAS)

# squared correlation between the response variable and the predicted values
cor(model.response(model.frame(model.strength.AVEL)),predict(model.strength.AVEL,type="response"))^2
cor(model.response(model.frame(model.strength.CLIB)),predict(model.strength.CLIB,type="response"))^2
cor(model.response(model.frame(model.strength.HCOM)),predict(model.strength.HCOM,type="response"))^2
cor(model.response(model.frame(model.strength.HHAL)),predict(model.strength.HHAL,type="response"))^2
cor(model.response(model.frame(model.strength.HPIC)),predict(model.strength.HPIC,type="response"))^2
cor(model.response(model.frame(model.strength.LPED)),predict(model.strength.LPED,type="response"))^2
cor(model.response(model.frame(model.strength.ROFF)),predict(model.strength.ROFF,type="response"))^2
cor(model.response(model.frame(model.strength.SGEN)),predict(model.strength.SGEN,type="response"))^2
cor(model.response(model.frame(model.strength.TMAS)),predict(model.strength.TMAS,type="response"))^2


# CLOSENESS
plot(model.closeness.AVEL)
plot(model.closeness.CLIB)
plot(model.closeness.HCOM)
plot(model.closeness.HHAL)
plot(model.closeness.HPIC)
plot(model.closeness.LPED)
plot(model.closeness.ROFF)
plot(model.closeness.SGEN)
plot(model.closeness.TMAS)

lattice::qqmath(model.closeness.AVEL)
lattice::qqmath(model.closeness.CLIB)
lattice::qqmath(model.closeness.HCOM)
lattice::qqmath(model.closeness.HHAL)
lattice::qqmath(model.closeness.HPIC)
lattice::qqmath(model.closeness.LPED)
lattice::qqmath(model.closeness.ROFF)
lattice::qqmath(model.closeness.SGEN)
lattice::qqmath(model.closeness.TMAS)

# squared correlation between the response variable and the predicted values
cor(model.response(model.frame(model.closeness.AVEL)),predict(model.closeness.AVEL,type="response"))^2
cor(model.response(model.frame(model.closeness.CLIB)),predict(model.closeness.CLIB,type="response"))^2
cor(model.response(model.frame(model.closeness.HCOM)),predict(model.closeness.HCOM,type="response"))^2
cor(model.response(model.frame(model.closeness.HHAL)),predict(model.closeness.HHAL,type="response"))^2
cor(model.response(model.frame(model.closeness.HPIC)),predict(model.closeness.HPIC,type="response"))^2
cor(model.response(model.frame(model.closeness.LPED)),predict(model.closeness.LPED,type="response"))^2
cor(model.response(model.frame(model.closeness.ROFF)),predict(model.closeness.ROFF,type="response"))^2
cor(model.response(model.frame(model.closeness.SGEN)),predict(model.closeness.SGEN,type="response"))^2
cor(model.response(model.frame(model.closeness.TMAS)),predict(model.closeness.TMAS,type="response"))^2


# NICHE OVERLAP
plot(model.niche.overlap.AVEL)
plot(model.niche.overlap.CLIB)
plot(model.niche.overlap.HCOM)
plot(model.niche.overlap.HHAL)
plot(model.niche.overlap.HPIC)
plot(model.niche.overlap.LPED)
plot(model.niche.overlap.ROFF)
plot(model.niche.overlap.SGEN)
plot(model.niche.overlap.TMAS)

lattice::qqmath(model.niche.overlap.AVEL)
lattice::qqmath(model.niche.overlap.CLIB)
lattice::qqmath(model.niche.overlap.HCOM)
lattice::qqmath(model.niche.overlap.HHAL)
lattice::qqmath(model.niche.overlap.HPIC)
lattice::qqmath(model.niche.overlap.LPED)
lattice::qqmath(model.niche.overlap.ROFF)
lattice::qqmath(model.niche.overlap.SGEN)
lattice::qqmath(model.niche.overlap.TMAS)

# squared correlation between the response variable and the predicted values
cor(model.response(model.frame(model.niche.overlap.AVEL)),predict(model.niche.overlap.AVEL,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.CLIB)),predict(model.niche.overlap.CLIB,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.HCOM)),predict(model.niche.overlap.HCOM,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.HHAL)),predict(model.niche.overlap.HHAL,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.HPIC)),predict(model.niche.overlap.HPIC,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.LPED)),predict(model.niche.overlap.LPED,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.ROFF)),predict(model.niche.overlap.ROFF,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.SGEN)),predict(model.niche.overlap.SGEN,type="response"))^2
cor(model.response(model.frame(model.niche.overlap.TMAS)),predict(model.niche.overlap.TMAS,type="response"))^2




```

```{r combine.plots}

full.model.plot <- full.plot.degree + full.plot.strength + full.plot.closeness + full.plot.nicheoverlap + 
  plot_layout(ncol = 4)

full.model.plot[[1]] = full.model.plot[[1]] + theme(legend.position="none") 
full.model.plot[[2]] = full.model.plot[[2]] + 
            theme(legend.position="none", axis.text.y = element_blank(), axis.ticks.y = element_blank()) 
full.model.plot[[3]] = full.model.plot[[3]] + 
            theme(legend.position="none", axis.text.y = element_blank(), axis.ticks.y = element_blank())
full.model.plot[[4]] = full.model.plot[[4]] + 
            theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())


full.model.plot <- full.plot.degree + full.plot.nicheoverlap + 
  plot_layout(ncol = 2)

full.model.plot[[1]] = full.model.plot[[1]] + theme(legend.position="none") 
full.model.plot[[2]] = full.model.plot[[2]] + 
            theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) 


```


# Structural Equation Models

```{r SEM}


#data.norm <- all.data %>% filter(Plant_sp == "ROFF")
data.norm <- na.omit(all.data)
data.norm <- as.data.frame(lapply((data.norm[, c(4, 8:18)]), range01))
cor(data.norm)


m1a <- lm(degree ~ N_flowers, data=data.norm)
(fit1a <-summary(m1a))


library(lavaan)

#simple regression using lavaan 
m1b <-   '
  # regressions
    degree ~ 1 + N_flowers
  # variance (optional)
    N_flowers ~~ N_flowers
'
fit1b <- sem(m1b, data=data.norm)
summary(fit1b)

#multiple regression using lavaan 

m2 <- '
  # regressions
    degree ~ 1 + N_flowers + sync_index_het
 # covariance
    N_flowers ~~ sync_index_con
'
fit2 <- sem(m2, data=data.norm)
summary(fit2)

#multivariate regression using lavaan 

m3a <- '
# regressions
N_flowers ~ 1 + Height_cm
weighted.degree ~ 1 + N_flowers + Height_cm + sync_index_het + sync_index_con + Cover_con + Cover_het
strength ~ 1 + N_flowers + Height_cm + sync_index_het + sync_index_con + Cover_con + Cover_het + weighted.degree + niche.overlap
weighted.closeness ~ 1 + N_flowers + Height_cm + sync_index_het + sync_index_con + Cover_con + Cover_het + weighted.degree
niche.overlap ~ 1 + N_flowers + Height_cm + sync_index_het + sync_index_con + Cover_con + Cover_het

'
fit3a <- sem(m3a, data=data.norm)
summary(fit3a)

inspect(fit3a, what="cor.all")
lavCor(fit3a)
resid(fit3a, "cor")



lavaanPlot(model = fit3a, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coefs = TRUE)

lavaanPlot(model = fit3a, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coefs = TRUE, sig = .05, stand=TRUE)


```

